### 2018-05-10 manuscript.rmd
fixed node support issue

  get_node_support = function(  tree, treeset, threshold=100 ){
    # Returns a vector corresponding to nodes in tree, with percent of trees
    # in treeset that contain the corresponding bipartition
    clades = prop.clades(tree, treeset) / length(treeset)
    nodes = c(rep(NA,length(tree$tip.label)), round(clades*100)) # Offset with NA values for tips
    nodes[ length(tree$tip.label) + 1 ] = NA # Set the root value to NA, not a robust way to find root but works in this case

@@

	support = as.numeric( BIspeciestree$node.label )
	support[ support > 99 ] = NA

	# pad tip values
	support = c( rep( NA, length( BIspeciestree$tip.label ) ), support )

>>>>

  get_node_support = function(  tree, treeset, threshold=100 ){
    # Returns a vector corresponding to nodes in tree, with percent of trees
    # in treeset that contain the corresponding bipartition
    clades = prop.clades(tree, treeset) / length(treeset)
    clades[is.na(clades)]<-0
    nodes = c(rep(NA,length(tree$tip.label)), round(clades*100)) # Offset with NA values for tips
    nodes[ length(tree$tip.label) + 1 ] = NA # Set the root value to NA, not a robust way to find root but works in this case

@@
